---
title: "Experiment 2 - Data Processing"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    code_download: true
    code_folding: hide
    hightlight: github
    theme: united
    css: "../../style/style.css"
    toc: true
    toc_float: true
    toc_collapsed: true
    includes:
      in_header: "../../style/header.html"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../../data_codebook/") })
---

```{r setup, include=FALSE}
require(knitr)
knitr::opts_chunk$set(echo = T, warning = F, cache = F)
options(width = 80)
options(scipen = 10)
source(here::here("01_analyses/00_functions/00_init_scripts.R"))
# source("../00_functions/osf_auth.R") # this line has to be commented out when reproducing this
source(here::here("01_analyses/00_functions/01_rmd_helpers.R"))
source(here::here("01_analyses/00_functions/03_data_helpers.R"))
run_local = FALSE
```



# Download Data from OSF

First we download the Raw Data file from OSF. 
It contains all participants who have (almost) completed the study and were compensated on prolific.
The prolific IDs have been replaced with numbers before uploading.

```{r download_raw_data}

if(run_local){
  # one-time only anonymization of data to store it on OSF after processing
  raw_data <- read.csv("../../../99_RAW_DATA/01_exp2/data.csv", stringsAsFactors = F)
  set.seed(1)
  subject_ids_old <- unique(raw_data$subject)
  subject_ids_new <- sample(1:length(unique(raw_data$subject)), replace = F)
  for(i in 1:nrow(raw_data)){
    raw_data$subject[i] <- subject_ids_new[which(raw_data$subject[i] == subject_ids_old)]
    raw_data$ppn[i] <- raw_data$subject[i]
  }
  raw_data$subject <- as.integer(raw_data$subject)
  raw_data$ppn <- as.integer(raw_data$ppn)
  write.table(raw_data, "../../../99_RAW_DATA/01_exp2/data_anom.csv", row.names = FALSE, sep = ",")
  raw_data_anom <- read.csv("../../../99_RAW_DATA/01_exp2/data_anom.csv")
  stopifnot(identical(raw_data, raw_data_anom))
  write.table(cbind(subject_ids_old, subject_ids_new), "../../../99_RAW_DATA/01_exp2/ident_file.csv", row.names = FALSE, sep = ",")
  rm(subject_ids_old, subject_ids_new)
}

osf_node <- osf_retrieve_node("9y38n") # retrieve OSF node
osf_RAW_datafolder <- osf_ls_files(osf_node, path = "RAW_DATA\\Exp2", n_max = Inf) # get data folder
raw_data <- osf_load_file(osf_RAW_datafolder$id[1], osf_RAW_datafolder$name[1], 
                          stringsAsFactors = F)

```


# Split Data

Now, we need to split the raw data file into its components (i.e. the different tasks).

## Single Food Evaluations

```{r extract_foodrating_data}
#extract food ratings
single_eval_data <- subset(raw_data, trial_type == "image-slider-response" & 
                             response_cat == "value")
# select relevant columns for rating data of single items
single_eval_data <- single_eval_data[,which(names(single_eval_data) %in% 
                                              c("rt", "response", "stim_name", 
                                                 "subject", "subject_nr", 
                                                 "trial_nr", "block"))]
# rename response to evaluation
names(single_eval_data)[which(names(single_eval_data) == "response")] <- 
  "evaluation"

# single_eval_data <- single_eval_data[which(single_eval_data$evaluation > -999),]

################################################################
# Variable Explanations:
## RT: response time for each rating
## evaluation: evaluation (0-200)
## stim_name: the respective item that was presented
## subject:  the subject-key that identifies unique participants
## trial_nr: the number of the respective trial
## block: which block is the rating from 
################################################################

# fix variable types
single_eval_data$evaluation <- as.numeric(single_eval_data$evaluation)

# clean stimulus names
for (i in 1:nrow(single_eval_data)){
  single_eval_data$stim_name[i] <- gsub('.png','',
                                        basename(single_eval_data$stim_name[i]))
}
```


### Data preview and codebook

`r ncol(single_eval_data)` relevant variables were extracted:

<div class="table-container">

```{r single_evaluation_codebook, echo = F}
vars_single_eval <- colnames(single_eval_data)
varexplanation_single_eval <- 
  c("response time for each evaluation", 
    "evaluation (0-200)", 
    "the respective item that was presented", 
    "the subject-key that identifies unique participants",
    "the number of the respective trial", 
    "which block is the rating from")

# Variable Explanations:
## RT: response time for each rating
## evaluation: evaluation (0-200)
## stim_name: the file-path of the respective item that was presented
## subject:  the subject-key that identifies unique participants
## trial_nr: the number of the respective trial
## block: which block is the rating from 

tcb_single_eval <- make_table(data.frame(cbind(vars_single_eval, 
                                               varexplanation_single_eval)))
tcb_single_eval <- set_header_labels(tcb_single_eval, 
                                     vars_single_eval = "variable", 
                               varexplanation_single_eval = "explanation")
tcb_single_eval
```

The data file looks like this:

<div class="table-container">
`r make_table(head(single_eval_data), ali = "right", aw = 2)`
</div>



## Single Food Confidence Ratings

```{r extract_foodconfidence_data}
#extract food ratings
single_conf_data <- subset(raw_data, trial_type == "image-slider-response" & 
                             response_cat == "confidence")
# select relevant columns for rating data of single items
single_conf_data <- single_conf_data[,which(names(single_conf_data) %in% 
                                              c("rt", "response", "stim_name", 
                                                 "subject", "subject_nr", 
                                                 "trial_nr", "block"))]
# rename response to evaluation
names(single_conf_data)[which(names(single_conf_data) == "response")] <- 
  "confidence"


################################################################
# Variable Explanations:
## RT: response time for each rating
## evaluation: evaluation (0-200)
## stim_name: the respective item that was presented
## subject:  the subject-key that identifies unique participants
## trial_nr: the number of the respective trial
## block: which block is the rating from 
################################################################

# fix variable types
single_conf_data$confidence <- as.numeric(single_conf_data$confidence)

# clean stimulus names
for (i in 1:nrow(single_conf_data)){
  single_conf_data$stim_name[i] <- gsub('.png','',
                                        basename(single_conf_data$stim_name[i]))
}
```


### Data preview and codebook

`r ncol(single_conf_data)` relevant variables were extracted:

<div class="table-container">

```{r single_confidence_codebook, echo = F}
vars_single_conf <- colnames(single_conf_data)
varexplanation_single_conf <- 
  c("response time for each confidence rating", 
    "confidence rating (0-200)", 
    "the respective item that was presented", 
    "the subject-key that identifies unique participants",
    "the number of the respective trial", 
    "which block is the rating from")

# Variable Explanations:
## RT: response time for each rating
## evaluation: evaluation (0-200)
## stim_name: the file-path of the respective item that was presented
## subject:  the subject-key that identifies unique participants
## trial_nr: the number of the respective trial
## block: which block is the rating from 

tcb_single_conf <- make_table(data.frame(cbind(vars_single_conf, 
                                               varexplanation_single_conf)))
tcb_single_conf <- set_header_labels(tcb_single_conf, 
                                     vars_single_conf = "variable", 
                               varexplanation_single_conf = "explanation")
tcb_single_conf
```

The data file looks like this:

<div class="table-container">
`r make_table(head(single_conf_data), ali = "right", aw = 2)`
</div>


## Basket Evaluations

```{r extract_basketrating_data}
#extract basket evaluations
basket_eval_data <- subset(raw_data, trial_type == "html-slider-response" & response_cat == "value")
# select relevant columns for rating data of single items
basket_eval_data <- basket_eval_data[,which(names(basket_eval_data) %in% 
                                              c("rt", "response", "stim_name", 
                                                "subject", "trial_nr",
                                                "rep_nr", "item1_value", 
                                                "item1_confidence", 
                                                "item1_valueCat", 
                                                "item1_confidenceCat",
                                                "item2_value", 
                                                "item2_confidence", 
                                                "item2_valueCat", 
                                                "item2_confidenceCat",
                                                "item3_value", 
                                                "item3_confidence", 
                                                "item3_valueCat", 
                                                "item3_confidenceCat",
                                                "item1_pos", "item2_pos", 
                                                "item3_pos", "item1_name", 
                                                "item2_name", "item3_name",
                                                "basket_cat", 
                                                "basket_value", 
                                                "basket_conf", 
                                                "basket_cluster", 
                                                "cluster_size", 
                                                "basket_nr" 
                                                ))]
# rename response to evaluation
names(basket_eval_data)[which(names(basket_eval_data) == "response")] <- 
  "evaluation"


# fix variable types
basket_eval_data$evaluation <- as.numeric(basket_eval_data$evaluation)

# rename baskets
for(i in 1:nrow(basket_eval_data)){
  
  # extract individual items of baskets
  # remove file path and concatenate them to single string
  # items should already be sorted but sorting is applied gain to be sure
  basket_eval_data$stim_name[i] <- paste(sort(as.vector(
    sapply(strsplit(basket_eval_data$stim_name[i], ","), 
           function(x) gsub('.png','',basename(x))))), collapse = "")
  basket_eval_data$item1_name[i] <- gsub('.png','',
                                      basename(basket_eval_data$item1_name[i]))
  basket_eval_data$item2_name[i] <- gsub('.png','',
                                      basename(basket_eval_data$item2_name[i]))
  basket_eval_data$item3_name[i] <- gsub('.png','',
                                      basename(basket_eval_data$item3_name[i]))
  
}

```


### Data preview and codebook

`r ncol(basket_eval_data)` relevant variables were extracted:

<div class="table-container">

```{r basket_evaluation_codebook, echo = F}
vars_basket_eval <- colnames(basket_eval_data)
varexplanation_basket_eval <- 
  c("response time for each rating", 
    "basket evaluation (0-200)", 
    "the items in the respective basket that was presented", 
    "the subject-key that identifies unique participants",
    "the number of the respective trial", 
    "which repetition of the rating is this? (1-3)",
    "valuation of the first item in basket ",
    "confidence-rating of the first item in basket",
    "valuation of the second item in basket ",
    "confidence-rating of the second item in basket",
    "valuation of the third item in basket ",
    "confidence-rating of the third item in basket",
    "Where was item 1 positioned when displaying the basket in this trial?",
    "Where was item 2 positioned when displaying the basket in this trial?",
    "Where was item 3 positioned when displaying the basket in this trial?",
    "Which item was item 1?",
    "Which item was item 2?",
    "Which item was item 3?",
    "which category is this basket (high vs. low in confidence)",
    "average value of items in the basket",
    "average confidence of items in the basket",
    "cluster number that the basket was from for specific participant",
    "size of the cluster",
    "basket number within cluster"
    )

tcb_basket_eval <- make_table(data.frame(cbind(vars_basket_eval, 
                                               varexplanation_basket_eval)))
tcb_basket_eval <- set_header_labels(tcb_basket_eval, 
                                     vars_basket_eval = "variable", 
                               varexplanation_basket_eval = "explanation")
tcb_basket_eval
```

The data file looks like this:

<div class="table-container">
`r make_table(head(basket_eval_data), ali = "right", aw = 2)`
</div>








## Basket Confidence Ratings

```{r extract_basketconfidence_data}
#extract basket evaluations
basket_conf_data <- subset(raw_data, trial_type == "html-slider-response" & response_cat == "confidence")
# select relevant columns for rating data of single items
basket_conf_data <- basket_conf_data[,which(names(basket_conf_data) %in% 
                                              c("rt", "response", "stim_name", 
                                                "subject", "trial_nr",
                                                "rep_nr", "item1_value", 
                                                "item1_confidence", 
                                                "item1_valueCat", 
                                                "item1_confidenceCat",
                                                "item2_value", 
                                                "item2_confidence", 
                                                "item2_valueCat", 
                                                "item2_confidenceCat",
                                                "item3_value", 
                                                "item3_confidence", 
                                                "item3_valueCat", 
                                                "item3_confidenceCat",
                                                "item1_pos", "item2_pos", 
                                                "item3_pos", "item1_name", 
                                                "item2_name", "item3_name",
                                                "basket_cat", 
                                                "basket_value", 
                                                "basket_conf", 
                                                "basket_cluster", 
                                                "cluster_size", 
                                                "basket_nr" 
                                                ))]
# rename response to evaluation
names(basket_conf_data)[which(names(basket_conf_data) == "response")] <- 
  "confidence"


# fix variable types
basket_conf_data$confidence <- as.numeric(basket_conf_data$confidence)

# rename baskets
for(i in 1:nrow(basket_conf_data)){
  
  # extract individual items of baskets
  # remove file path and concatenate them to single string
  # items should already be sorted but sorting is applied gain to be sure
  basket_conf_data$stim_name[i] <- paste(sort(as.vector(
    sapply(strsplit(basket_conf_data$stim_name[i], ","), 
           function(x) gsub('.png','',basename(x))))), collapse = "")
  basket_conf_data$item1_name[i] <- gsub('.png','',
                                      basename(basket_conf_data$item1_name[i]))
  basket_conf_data$item2_name[i] <- gsub('.png','',
                                      basename(basket_conf_data$item2_name[i]))
  basket_conf_data$item3_name[i] <- gsub('.png','',
                                      basename(basket_conf_data$item3_name[i]))
  
}

```


### Data preview and codebook

`r ncol(basket_conf_data)` relevant variables were extracted:

<div class="table-container">

```{r basket_confidence_codebook, echo = F}
vars_basket_conf <- colnames(basket_conf_data)
varexplanation_basket_conf <- 
  c("response time for each rating", 
    "basket confidence (0-200)", 
    "the items in the respective basket that was presented", 
    "the subject-key that identifies unique participants",
    "the number of the respective trial", 
    "which repetition of the rating is this? (1-3)",
    "valuation of the first item in basket ",
    "confidence-rating of the first item in basket",
    "valuation of the second item in basket ",
    "confidence-rating of the second item in basket",
    "valuation of the third item in basket ",
    "confidence-rating of the third item in basket",
    "Where was item 1 positioned when displaying the basket in this trial?",
    "Where was item 2 positioned when displaying the basket in this trial?",
    "Where was item 3 positioned when displaying the basket in this trial?",
    "Which item was item 1?",
    "Which item was item 2?",
    "Which item was item 3?",
    "which category is this basket (high vs. low in confidence)",
    "average value of items in the basket",
    "average confidence of items in the basket",
    "cluster number that the basket was from for specific participant",
    "size of the cluster",
    "basket number within cluster"
    )

tcb_basket_conf <- make_table(data.frame(cbind(vars_basket_conf, 
                                               varexplanation_basket_conf)))
tcb_basket_conf <- set_header_labels(tcb_basket_conf, 
                                     vars_basket_conf = "variable", 
                               varexplanation_basket_conf = "explanation")
tcb_basket_conf
```

The data file looks like this:

<div class="table-container">
`r make_table(head(basket_conf_data), ali = "right", aw = 2)`
</div>



# Check whether all data was extracted

```{r test_data_complete}
stopifnot(nrow(single_eval_data)+nrow(single_conf_data)+
            nrow(basket_eval_data)+nrow(basket_conf_data) == nrow(raw_data))
```



# Add Evaluations and Confidence to respective other data frames

To make analyses easier, the evaluations from the food-evaluation and basket-evaluation files will be added to the respective confidence files and vice versa.

```{r add_vars_to_eval_con}

# make row identifiers
## single evaluations
single_eval_data$r_ident <- paste(single_eval_data$subject, single_eval_data$stim_name, single_eval_data$trial_nr, sep = "-")
### test for identical length
stopifnot(length(unique(single_eval_data$r_ident)) == nrow(single_eval_data)) 
## single confidence
single_conf_data$r_ident <- paste(single_conf_data$subject, single_conf_data$stim_name, single_conf_data$trial_nr, sep = "-")
### test for identical length
stopifnot(length(unique(single_conf_data$r_ident)) == nrow(single_conf_data))
## basket evaluation
basket_eval_data$r_ident <- paste(basket_eval_data$subject, basket_eval_data$stim_name, basket_eval_data$trial_nr, sep = "-")
### test for identical length
stopifnot(length(unique(basket_eval_data$r_ident)) == nrow(basket_eval_data))
## basket confidence
basket_conf_data$r_ident <- paste(basket_conf_data$subject, basket_conf_data$stim_name, basket_conf_data$trial_nr, sep = "-")
### test for identical length
stopifnot(length(unique(basket_conf_data$r_ident)) == nrow(basket_conf_data))

#add relevant columns
single_eval_data <- merge(single_eval_data, single_conf_data[, c("r_ident", "confidence")], by="r_ident")
single_conf_data <- merge(single_conf_data, single_eval_data[, c("r_ident", "evaluation")], by="r_ident")

basket_eval_data <- merge(basket_eval_data, basket_conf_data[, c("r_ident", "confidence")], by="r_ident")
basket_conf_data <- merge(basket_conf_data, basket_eval_data[, c("r_ident", "evaluation")], by="r_ident")
```


# Add value diversity and mean confidence rating variables

```{r add_IVs}
for(i in 1:nrow(basket_eval_data)){
  basket_eval_data$value_sd[i] <- sd(c(basket_eval_data$item1_value[i], basket_eval_data$item2_value[i], basket_eval_data$item3_value[i]))
  basket_eval_data$confidence_mean[i] <- mean(c(basket_eval_data$item1_confidence[i], basket_eval_data$item2_confidence[i], basket_eval_data$item3_confidence[i]))
  basket_eval_data$basket_confidence_cat[i] <- ifelse(basket_eval_data$basket_cat[i] %in% c("Chigh_Dlow", "Chigh_Dhigh"), "high", "low")
  basket_eval_data$basket_diversity_cat[i] <- ifelse(basket_eval_data$basket_cat[i] %in% c("Chigh_Dhigh", "Clow_Dhigh"), "high", "low")
  
}

for(i in 1:nrow(basket_conf_data)){
  basket_conf_data$value_sd[i] <- sd(c(basket_conf_data$item1_value[i], basket_conf_data$item2_value[i], basket_conf_data$item3_value[i]))
  basket_conf_data$confidence_mean[i] <- mean(c(basket_conf_data$item1_confidence[i], basket_conf_data$item2_confidence[i], basket_conf_data$item3_confidence[i]))
  basket_conf_data$basket_confidence_cat[i] <- ifelse(basket_conf_data$basket_cat[i] %in% c("Chigh_Dlow", "Chigh_Dhigh"), "high", "low")
  basket_conf_data$basket_diversity_cat[i] <- ifelse(basket_conf_data$basket_cat[i] %in% c("Chigh_Dhigh", "Clow_Dhigh"), "high", "low")
  
}
```

# Add markers for preregistered exclusion criteria

```{r mark_exclusions}
pp_exclude_list <- c()

for(i in unique(single_eval_data$subject)){
  tmp_dat <- subset(single_eval_data, subject == i)
  tmp_inter <- hdi(tmp_dat$evaluation, credMass = .79, allowSplit = T)
  if(abs(tmp_inter[1]-tmp_inter[2]) <= 10){
    pp_exclude_list <- append(pp_exclude_list, i)
  }
}

for(i in unique(single_conf_data$subject)){
  tmp_dat <- subset(single_conf_data, subject == i)
  tmp_inter <- hdi(tmp_dat$confidence, credMass = .79, allowSplit = T)
  if(abs(tmp_inter[1]-tmp_inter[2]) <= 10){
    pp_exclude_list <- append(pp_exclude_list, i)
  }
}

pp_exclude_list <- unique(pp_exclude_list)


for(i in 1:nrow(single_eval_data)){
  single_eval_data$prereg_exclusion[i] <- 
    ifelse(single_eval_data$subject[i] %in% pp_exclude_list, 1, 0)
}


for(i in 1:nrow(single_conf_data)){
  single_conf_data$prereg_exclusion[i] <- 
    ifelse(single_conf_data$subject[i] %in% pp_exclude_list, 1, 0)
}

for(i in 1:nrow(basket_eval_data)){
  basket_eval_data$prereg_exclusion[i] <- 
    ifelse(basket_eval_data$subject[i] %in% pp_exclude_list, 1, 0)
}

for(i in 1:nrow(basket_conf_data)){
  basket_conf_data$prereg_exclusion[i] <- 
    ifelse(basket_conf_data$subject[i] %in% pp_exclude_list, 1, 0)
}
```


# Upload data to OSF


```{r upload_to_osf, output = FALSE, eval = FALSE}
# mark upload folder
processed_data_dir <- osf_ls_files(osf_node)[which(osf_ls_files(osf_node)$name == "processed_data"),]

# single evaluations
write.csv(single_eval_data, "single_eval_data_exp2.csv")
osf_upload_file(osf_node = osf_node, remote_path = "single_eval_data_exp2.csv",
                local_path = "single_eval_data_exp2.csv", conflicts = "overwrite",
                local_file_remove = TRUE, osf_direct_dir = processed_data_dir)

# single confidence
write.csv(single_conf_data, "single_conf_data_exp2.csv")
osf_upload_file(osf_node = osf_node, remote_path = "single_conf_data_exp2.csv",
                local_path = "single_conf_data_exp2.csv", conflicts = "overwrite",
                local_file_remove = TRUE, osf_direct_dir = processed_data_dir)

# basket evaluations
write.csv(basket_eval_data, "basket_eval_data_exp2.csv")
osf_upload_file(osf_node = osf_node, remote_path = "basket_eval_data_exp2.csv",
                local_path = "basket_eval_data_exp2.csv", conflicts = "overwrite",
                local_file_remove = TRUE, osf_direct_dir = processed_data_dir)

# basket confidence
write.csv(basket_conf_data, "basket_conf_data_exp2.csv")
osf_upload_file(osf_node = osf_node, remote_path = "basket_conf_data_exp2.csv",
                local_path = "basket_conf_data_exp2.csv", conflicts = "overwrite",
                local_file_remove = TRUE, osf_direct_dir = processed_data_dir)
```