---
title: "Experiment 4 - Data Processing"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    code_download: true
    code_folding: hide
    hightlight: github
    theme: united
    css: "../../style/style.css"
    toc: true
    toc_float: true
    toc_collapsed: true
    includes:
      in_header: "../../style/header.html"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../../data_codebook/") })
---

```{r setup, include=FALSE}
require(knitr)
knitr::opts_chunk$set(echo = T, warning = F, cache = F)
options(width = 80)
options(scipen = 10)
source(here::here("01_analyses/00_functions/00_init_scripts.R"))
# source("../00_functions/osf_auth.R") # this line has to be commented out when reproducing this
source(here::here("01_analyses/00_functions/01_rmd_helpers.R"))
source(here::here("01_analyses/00_functions/03_data_helpers.R"))
run_local = FALSE
```



# Download Data from OSF

First we download the Raw Data file from OSF. 
It contains all participants who have (almost) completed the study and were compensated on prolific.
The prolific IDs have been replaced with numbers before uploading.

```{r download_raw_data}

if(run_local == TRUE){
  raw_data <- read.csv(here::here("01_analyses/99_RAW_DATA/03_exp4/data.csv"), stringsAsFactors = F)
  raw_data$trial_type[which(raw_data$duplicate == "true")] <- "html-slider-response"


  # give participants a number
  subject_nrs <- c(1:length(unique(raw_data$ppn)))
  set.seed(pp_rnd_seed) # seed is only saved locally.
  subject_nrs <- sample(subject_nrs)
  for(i in 1:nrow(raw_data)){
    raw_data$subject_nr[i] <- subject_nrs[which(unique(raw_data$ppn) == raw_data$ppn[i])]
  }
  raw_data <- raw_data[,-which(colnames(raw_data) %in% c("subject", "ppn", "Timestamp", "Age", "Gender", "internal_node_id", "Server_timestamp",
                                                        "timestamp", "server_timestamp", "time_elapsed", "age", "gender"))]

  raw_data <- raw_data[order(raw_data$subject_nr), ]

  write.table(raw_data, here::here("01_analyses/99_RAW_DATA/03_exp4/data_anom.csv"), row.names = FALSE, sep = ",")

} else {
  osf_node <- osf_retrieve_node("9y38n") # retrieve OSF node
  osf_RAW_datafolder <- osf_ls_files(osf_node, path = "RAW_DATA\\Exp4", n_max = Inf) # get data folder
  raw_data <- osf_load_file(osf_RAW_datafolder$id[1], osf_RAW_datafolder$name[1], 
                            stringsAsFactors = FALSE)
}
```


# Split Data

Now, we need to split the raw data file into its components (i.e. the different tasks).

## Single Food Evaluations

```{r extract_foodrating_data}
#extract food ratings
item_eval_data <- subset(raw_data, trial_type == "distribution-builder" & 
                             response_cat == "rating" & stimulus_type == "item")


# select relevant columns for rating data of single items
item_eval_data <- item_eval_data[,which(names(item_eval_data) %in% 
                                              c("rt", "response", "stim_name", 
                                                 "subject_nr", 
                                                 "trial_nr"))]
for(i in 1:nrow(item_eval_data)){
  item_eval_data$response[i] <- strsplit(item_eval_data$response[i], "_")[[1]][2]

}
# rename response to evaluation
names(item_eval_data)[which(names(item_eval_data) == "response")] <- 
  "evaluation"

# fix variable types
item_eval_data$evaluation <- as.numeric(item_eval_data$evaluation)
item_eval_data$evaluation <- item_eval_data$evaluation*50 # transform to eurocent scale


# clean stimulus names and make price columns
for (i in 1:nrow(item_eval_data)){
  item_eval_data$stim_name[i] <- gsub('.png','',
                                        basename(item_eval_data$stim_name[i]))
  item_eval_data$price_exact[i] <- as.numeric(sub(".*(\\d+{4}).*$", "\\1", item_eval_data$stim_name[i]))
  item_eval_data$price_rounded[i] <- plyr::round_any(item_eval_data$price_exact[i], 50) 
}
```


### Data preview and codebook

`r ncol(item_eval_data)` relevant variables were extracted:

<div class="table-container">

```{r single_evaluation_codebook, echo = F}
vars_single_eval <- colnames(item_eval_data)
varexplanation_single_eval <- 
  c("response time for each evaluation", 
    "evaluation (0-2500 eurocents)", 
    "the respective item that was presented", 
    "the number of the respective trial",
    "the subject-number that identifies unique participants",
    "the real price of the item presented",
    "the price of the item rounded to response scale"
    )

tcb_single_eval <- make_table(data.frame(cbind(vars_single_eval, 
                                               varexplanation_single_eval)))
tcb_single_eval <- set_header_labels(tcb_single_eval, 
                                     vars_single_eval = "variable", 
                               varexplanation_single_eval = "explanation")
tcb_single_eval
```

The data file looks like this:

<div class="table-container">
`r make_table(head(item_eval_data), ali = "right", aw = 2)`
</div>

## Basket Evaluations

```{r extract_basketrating_data}
#extract basket evaluations
basket_eval_data <- subset(raw_data, trial_type == "distribution-builder" & response_cat == "rating" & stimulus_type == "basket")
# select relevant columns for rating data of single items
basket_eval_data <- basket_eval_data[,which(names(basket_eval_data) %in% 
                                              c("rt", "response",
                                                "stim_name", 
                                                "subject_nr", "trial_nr",
                                                "item1_value", 
                                                "item1_value_ex", 
                                                "item1_confidence", 
                                                "item1_valueCat", 
                                                "item1_confidenceCat",
                                                "item2_value", 
                                                "item2_value_ex", 
                                                "item2_confidence", 
                                                "item2_valueCat", 
                                                "item2_confidenceCat",
                                                "item3_value", 
                                                "item3_value_ex", 
                                                "item3_confidence", 
                                                "item3_valueCat", 
                                                "item3_confidenceCat",
                                                "item1_pos", "item2_pos", 
                                                "item3_pos", "item1_name", 
                                                "item2_name", "item3_name",
                                                "basket_cat", 
                                                "basket_value", 
                                                "basket_value_ex", 
                                                "basket_conf", 
                                                "basket_cluster", 
                                                "cluster_size", 
                                                "basket_matching_var", 
                                                "basket_nr"
                                                ))]
for(i in 1:nrow(basket_eval_data)){
  basket_eval_data$response[i] <- strsplit(basket_eval_data$response[i], "_")[[1]][2]

}

# rename response to evaluation
names(basket_eval_data)[which(names(basket_eval_data) == "response")] <- 
  "evaluation"


basket_eval_data$evaluation <- as.numeric(basket_eval_data$evaluation)
basket_eval_data$evaluation <- basket_eval_data$evaluation*150 # transform to eurocent scale

# rename baskets
for(i in 1:nrow(basket_eval_data)){
  
  # extract individual items of baskets
  # remove file path and concatenate them to single string
  # items should already be sorted but sorting is applied gain to be sure
  basket_eval_data$stim_name[i] <- paste(sort(as.vector(
    sapply(strsplit(basket_eval_data$stim_name[i], ","), 
           function(x) gsub('.png','',basename(x))))), collapse = "")
  basket_eval_data$item1_name[i] <- gsub('.png','',
                                      basename(basket_eval_data$item1_name[i]))
  basket_eval_data$item2_name[i] <- gsub('.png','',
                                      basename(basket_eval_data$item2_name[i]))
  basket_eval_data$item3_name[i] <- gsub('.png','',
                                      basename(basket_eval_data$item3_name[i]))
  
  basket_eval_data$price_exact[i] <- (as.numeric(sub(".*(\\d+{4}).*$", "\\1", basket_eval_data$item1_name[i]))+
                                      as.numeric(sub(".*(\\d+{4}).*$", "\\1", basket_eval_data$item2_name[i]))+
                                      as.numeric(sub(".*(\\d+{4}).*$", "\\1", basket_eval_data$item3_name[i]))
                                    )
  
    basket_eval_data$price_rounded[i] <- (plyr::round_any(as.numeric(sub(".*(\\d+{4}).*$", "\\1", basket_eval_data$item1_name[i])), 50)+
                                      plyr::round_any(as.numeric(sub(".*(\\d+{4}).*$", "\\1", basket_eval_data$item2_name[i])), 50)+
                                      plyr::round_any(as.numeric(sub(".*(\\d+{4}).*$", "\\1", basket_eval_data$item3_name[i])), 50)
                                    )
  
}
```

### Data preview and codebook

`r ncol(basket_eval_data)` relevant variables were extracted:

<div class="table-container">

```{r single_basketuation_codebook, echo = F}
vars_single_basket <- colnames(basket_eval_data)
varexplanation_single_basket <- 
  c("response time for each rating", 
    "basket evaluation (0-7500 cents)", 
    "the items in the respective basket that was presented", 
    "the number of the respective trial", 
    "Where was item 1 positioned when displaying the basket in this trial?",
    "Where was item 2 positioned when displaying the basket in this trial?",
    "Where was item 3 positioned when displaying the basket in this trial?",
    "Which item was item 1?",
    "Which item was item 2?",
    "Which item was item 3?",
    "which category is this basket (high or low in either value consistency of items (rating_sd) or extremity of items (evaluation_ex))",
    "average valuation of items in the basket",
    "average value extremity of items in basket ",
    "cluster number that the basket was from for specific participant",
    "cluster size of the cluster",
    "basket number within cluster",
    "matching variable that was used for the basket (consistency or value extremity)",
    "the subject number that distinguishes participants",
    "sum of prices of items in basket",
    "price rounded to resolution of response scale"
    )

tcb_single_basket <- make_table(data.frame(cbind(vars_single_basket, 
                                               varexplanation_single_basket)))
tcb_single_basket <- set_header_labels(tcb_single_basket, 
                                     vars_single_basket = "variable", 
                               varexplanation_single_basket = "explanation")
tcb_single_basket
```

The data file looks like this:

<div class="table-container">
`r make_table(head(basket_eval_data), ali = "right", aw = 2)`
</div>








## Basket Confidence Ratings

```{r extract_basketconfidence_data}

#extract basket evaluations
basket_conf_data <- subset(raw_data, trial_type == "html-slider-response" & response_cat == "confidence" & stimulus_type == "basket")
# select relevant columns for rating data of single items
basket_conf_data <- basket_conf_data[,which(names(basket_conf_data) %in% 
                                              c("rt", "response",
                                                "stim_name", 
                                                "subject_nr", "trial_nr",
                                                "item1_avg_rating", 
                                                "item1_avg_rating_ex", 
                                                "item1_rating_sd", 
                                                "item2_avg_rating", 
                                                "item2_avg_rating_ex", 
                                                "item2_rating_sd", 
                                                "item3_avg_rating", 
                                                "item3_avg_rating_ex", 
                                                "item3_rating_sd", 
                                                "item1_pos", "item2_pos", 
                                                "item3_pos", "item1_name", 
                                                "item2_name", "item3_name",
                                                "basket_cat", 
                                                "basket_value", 
                                                "basket_value_ex", 
                                                "basket_rating_sd", 
                                                "basket_cluster", 
                                                "cluster_size", 
                                                "basket_matching_var", 
                                                "basket_nr" ,
                                                "duplicate" 
                                                ))]
# rename response to evaluation
names(basket_conf_data)[which(names(basket_conf_data) == "response")] <- 
  "confidence"


# fix variable types
basket_conf_data$confidence <- as.numeric(basket_conf_data$confidence)

# rename baskets
basket_conf_data$evaluation <- NA
for(i in 1:nrow(basket_conf_data)){
  
  # extract individual items of baskets
  # remove file path and concatenate them to single string
  # items should already be sorted but sorting is applied gain to be sure
  basket_conf_data$stim_name[i] <- paste(sort(as.vector(
    sapply(strsplit(basket_conf_data$stim_name[i], ","), 
           function(x) gsub('.png','',basename(x))))), collapse = "")
  basket_conf_data$item1_name[i] <- gsub('.png','',
                                      basename(basket_conf_data$item1_name[i]))
  basket_conf_data$item2_name[i] <- gsub('.png','',
                                      basename(basket_conf_data$item2_name[i]))
  basket_conf_data$item3_name[i] <- gsub('.png','',
                                      basename(basket_conf_data$item3_name[i]))
  
  basket_conf_data$price_exact[i] <- (as.numeric(sub(".*(\\d+{4}).*$", "\\1", basket_conf_data$item1_name[i]))+
                                      as.numeric(sub(".*(\\d+{4}).*$", "\\1", basket_conf_data$item2_name[i]))+
                                      as.numeric(sub(".*(\\d+{4}).*$", "\\1", basket_conf_data$item3_name[i]))
                                    )
  
    basket_conf_data$price_rounded[i] <- (plyr::round_any(as.numeric(sub(".*(\\d+{4}).*$", "\\1", basket_conf_data$item1_name[i])), 50)+
                                      plyr::round_any(as.numeric(sub(".*(\\d+{4}).*$", "\\1", basket_conf_data$item2_name[i])), 50)+
                                      plyr::round_any(as.numeric(sub(".*(\\d+{4}).*$", "\\1", basket_conf_data$item3_name[i])), 50)
                                    )
  
}
basket_conf_nodupes <- subset(basket_conf_data, duplicate == "false")
for(i in 1:nrow(basket_conf_nodupes)){
  basket_conf_nodupes$evaluation[i] <-  subset(basket_eval_data, subject_nr == basket_conf_nodupes$subject_nr[i] & stim_name == basket_conf_nodupes$stim_name[i])$evaluation
}
for(i in 1:nrow(basket_conf_data)){
  basket_conf_data$evaluation[i] <-  subset(basket_conf_nodupes, subject_nr == basket_conf_data$subject_nr[i] & stim_name == basket_conf_data$stim_name[i])$evaluation
}


basket_conf_data_dupes <- which(basket_conf_data$duplicate  == "true")
for(i in basket_conf_data_dupes){
  sub <- basket_conf_data$subject_nr[i]
  bask <- basket_conf_data$stim_name[i]
  orig_basket <- subset(basket_conf_nodupes, subject_nr == sub & stim_name == bask)
  basket_conf_data$confidence[i] <- orig_basket$confidence
  basket_conf_data$rt[i] <- orig_basket$rt
  basket_conf_data$trial_nr[i] <- orig_basket$trial_nr
}

```

### Data preview and codebook

`r ncol(basket_conf_data)` relevant variables were extracted:

<div class="table-container">

```{r basket_confidence_codebook, echo = F}
vars_basket_conf <- colnames(basket_conf_data)
varexplanation_basket_conf <- 
  c("response time for each rating", 
    "basket confidence (0-200)", 
    "the items in the respective basket that was presented", 
    "the number of the respective trial", 
    "valuation of the first item in basket ",
    "value extremity of the first item in basket",
    "consistency of ratings of the first item in basket",
    "valuation of the second item in basket ",
    "value extremity of the second item in basket ",
    "consistency of ratings of the second item in basket",
    "valuation of the third item in basket ",
    "value extremity of the third item in basket ",
    "consistency of ratings of the third item in basket",
    "Where was item 1 positioned when displaying the basket in this trial?",
    "Where was item 2 positioned when displaying the basket in this trial?",
    "Where was item 3 positioned when displaying the basket in this trial?",
    "Which item was item 1?",
    "Which item was item 2?",
    "Which item was item 3?",
    "which category is this basket (high or low in either value consistency of items (rating_sd) or extremity of items (evaluation_ex))",
    "average valuation of items in the basket",
    "average value extremity of items in basket ",
    "consistency of single items in the basket",
    "cluster number that the basket was from for specific participant",
    "cluster size of the cluster",
    "basket number within cluster",
    "matching variable that was used for the basket (consistency or value extremity)",
    "indicates whether rating was restored from a 'duplicate' meaning that if a basket was present in both matching conditions, it was only rated once",
    "the subject number that distinguishes participants",
    "basket evaluation (0 - 7500 eurocents)",
    "sum of prices of items in basket",
    "price rounded to resolution of response scale"
    )

tcb_basket_conf <- make_table(data.frame(cbind(vars_basket_conf, 
                                               varexplanation_basket_conf)))
tcb_basket_conf <- set_header_labels(tcb_basket_conf, 
                                     vars_basket_conf = "variable", 
                               varexplanation_basket_conf = "explanation")
tcb_basket_conf
```

The data file looks like this:

<div class="table-container">
`r make_table(head(basket_conf_data), ali = "right", aw = 2)`
</div>



# Check whether all data was extracted

```{r test_data_complete}


sub_notin <- raw_data[which(row.names(raw_data) %in% 
                              c(row.names(item_eval_data), 
                                row.names(basket_eval_data), 
                                row.names(basket_conf_data)) == FALSE),]

stopifnot(all(sub_notin$response_cat == "auction" | sub_notin$response_cat == "auction_output" | (sub_notin$response_cat == "rating" & sub_notin$dupblicate == "true")))
```



# Add Evaluations and Confidence to respective other data frames

To make analyses easier, the evaluations from the item-evaluation and basket-evaluation files will be added to the respective confidence files and vice versa.

```{r add_vars_to_eval_con}

# make row identifiers
## single evaluations
item_eval_data$r_ident <- paste(item_eval_data$subject, item_eval_data$stim_name, item_eval_data$trial_nr, sep = "-")
### test for identical length
stopifnot(length(unique(item_eval_data$r_ident)) == nrow(item_eval_data)) 

## basket evaluation
basket_eval_data$r_ident <- paste(basket_eval_data$subject, basket_eval_data$stim_name, basket_eval_data$basket_matching_var, sep = "-")
### test for identical length
stopifnot(length(unique(basket_eval_data$r_ident)) == nrow(basket_eval_data))
## basket confidence
basket_conf_data$r_ident <- paste(basket_conf_data$subject, basket_conf_data$stim_name, basket_conf_data$basket_matching_var, sep = "-")
### test for identical length
stopifnot(length(unique(basket_conf_data$r_ident)) == nrow(basket_conf_data))


# move attention check data to other df
atcheck_data <- subset(item_eval_data, substr(stim_name, 1, 3) == "000")
```


# Add value diversity and mean confidence rating variables

```{r add_IVs}
for(i in 1:nrow(basket_eval_data)){
  basket_eval_data$value_sd[i] <- sd(c(basket_eval_data$item1_value[i]*50, basket_eval_data$item2_value[i]*50, basket_eval_data$item3_value[i]*50))
  
}

for(i in 1:nrow(basket_conf_data)){
  basket_conf_data$value_sd[i] <- sd(c(basket_conf_data$item1_avg_rating[i]*50, basket_conf_data$item2_avg_rating[i]*50, basket_conf_data$item3_avg_rating[i]*50))
}
```

# Add markers for preregistered exclusion criteria

```{r mark_exclusions}
pp_exclude_list <- c()

for(i in unique(item_eval_data$subject_nr)){
  tmp_dat <- subset(item_eval_data, subject_nr == i)
  tmp_inter <- hdi(tmp_dat$evaluation, credMass = .79, allowSplit = T)
  if(abs(tmp_inter[1]-tmp_inter[2]) <= 125){
    pp_exclude_list <- append(pp_exclude_list, i)
  }
}

atfails <- atcheck_data[which(atcheck_data$evaluation != atcheck_data$price_rounded),]
atfails_subject <- atcheck_data$subject_nr[which(atcheck_data$evaluation != atcheck_data$price_rounded)]
atfails_subject <- names(which(table(atfails_subject) > 1))

pp_exclude_list <- append(unique(pp_exclude_list), atfails_subject)


for(i in 1:nrow(item_eval_data)){
  item_eval_data$prereg_exclusion[i] <- 
    ifelse(item_eval_data$subject_nr[i] %in% pp_exclude_list, 1, 0)
}



for(i in 1:nrow(basket_eval_data)){
  basket_eval_data$prereg_exclusion[i] <- 
    ifelse(basket_eval_data$subject_nr[i] %in% pp_exclude_list, 1, 0)
}

for(i in 1:nrow(basket_conf_data)){
  basket_conf_data$prereg_exclusion[i] <- 
    ifelse(basket_conf_data$subject_nr[i] %in% pp_exclude_list, 1, 0)
}
```


# Upload data to OSF


```{r upload_to_osf, output = FALSE, eval = FALSE} 
# mark upload folder 
processed_data_dir <- osf_ls_files(osf_node)[which(osf_ls_files(osf_node)$name == "processed_data"),]

# single evaluations 
write.csv(item_eval_data, "item_eval_data_exp4.csv") 
osf_upload(processed_data_dir, 
          path = "item_eval_data_exp4.csv", conflicts = "overwrite")

# basket evaluations 
write.csv(basket_eval_data, "basket_eval_data_exp4.csv") 
osf_upload(processed_data_dir, 
          path = "basket_eval_data_exp4.csv", conflicts = "overwrite")

# basket confidence 
write.csv(basket_conf_data, "basket_conf_data_exp4.csv")
osf_upload(processed_data_dir, 
          path = "basket_conf_data_exp4.csv", conflicts = "overwrite")
```
